\emoji{black-medium-small-square}~~{\color{black}\textbf{Argonne National Laboratory} \hfill  \textbf{Chicago, IL, USA}}\par
\begin{itemize}
    \item
        \textbf{Staff Scientist}
        \hfill  {Oct 2019 -- Sep 2022} \par
        \begin{enumerate}
<<<<<<< HEAD
            \item Led the development and worked on \textbf{first demonstration} of the lens-less MR-BCDI imaging technique.
            \item Led design of future experiments at DoE facilities with physics-based signal processing techniques.
            \item Led the multi-scale X-ray imaging approach for materials in difficult-to-access environments (APS, ESRF).
            \item Raised research funding (ANL LDRD) and led teams to run early-stage projects at synchrotron facilities.
            \item Proposed and executed successful synchrotron experiments (US, France).
            \item Published in high-impact journals, mentorship, organized/chaired international workshops.
=======
            \item Led the computational development and worked on the \textbf{first demonstration} of the lens-less MR-BCDI imaging technique.
            \item Led the design of future experiments at DoE facilities with physics-based signal processing techniques.
            \item Led the multi-scale X-ray imaging approach for materials in difficult-to-access environments.
            \item Raised \$900k seed funding for computational R\&D and novel microscopy infrastructure. 
            \item Proposed, executed novel proofs of concept in materials imaging (US, France).
            \item Published in high-impact journals, mentored junior researchers, organized/chaired international workshops.
>>>>>>> newtheme
        \end{enumerate}
    \item
        \textbf{Postdoctoral researcher}
        \hfill  {Jan 2017 -- Sep 2019} \par
        \begin{enumerate}
            \item \textbf{First demonstration} of multi-scale, high-energy coherent diffraction imaging (HEDM) of 3D materials.
        \end{enumerate}
\end{itemize}